---
title: "FS12a"
author: "Julian Trachsel"
date: "3/28/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## FS12a/ Alternatives to ABX (nursery)

Two main cohorts presented here. 
 1) NADC - Salmonella infection - 
     * 16S rRNA gene amplicon data at D0, D23
     * 1 pig per pen from all treatments
     * Then Xfered to NADC for Salmonella challenge
         * only Control, RPS, Acid, Zn+Cu, RCS, Bglu transfered
 2) Nursery Necropsy cohort
     * 

```{r }

FS12a_NMDS[[1]] %>% ggplot(aes(x=MDS1, y=MDS2)) +
  geom_point(aes(color=day), size=2)+
  geom_segment(aes(xend=centroidX, yend=centroidY, color=day)) +
  geom_point(data=labbies,aes(x=centroidX, y=centroidY, fill=treatment, shape=tissue), size=3, inherit.aes = FALSE)+     scale_shape_manual(values = c(21, 24)) +
  guides(fill = guide_legend(override.aes=list(shape=21)))


global_adon
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
